### 2017-07-07 inference.tex
Edits.

The correspondence between the inference rules and the RG judgment of
Sec.~\ref{sec:reasoning} is stated thus\footnote{The proof can be found in
the supplementary material.}:
\begin{theorem}
\label{thm:inference-sound}
  \emph{Forall} i,$R$,$I$,$c$,$\F$, if $\stable(\R,I)$ and $c \elabsto \F$,
  then:\\\vspace*{-0.2cm}
  \begin{smathpar}
  \begin{array}{c}
  \R \vdash \hoare{\lambda(\stl,\stg).~\stl=\emptyset \conj
  I(\stg)}{~c~}{\lambda(\stl,\stg).\stl = \F(\emptyset,\stg)}
  \end{array}
  \end{smathpar}
\end{theorem}
\noindent where the set expression $\F(\emptyset,\stg)$ has a natural
interpretation as discussed below.
% Where, ${\sf true} = \lambda(\stl,\stg).~true$ and $\stable(\R,I)
% \Leftrightarrow \forall\stl,\stg,\stg'. I(\stg) \conj
% \R(\stl,\stg,\stg') \Rightarrow \I(\stg')$.

@@

Theorem~\ref{thm:inference-sound} lets us replace the local judgment
of the \rulelabel{RG-Txn} rule (Fig.~\ref{fig:rg-rules}) by a state
transformer inference judgment. The soundness of a transaction's guarantee can now
be established w.r.t the effect $\F$ of the body. The
\rulelabel{RG-Txn} rule so updated is shown
below:
\begin{smathpar}
\begin{array}{c}
\RULE
{
  \stable(R,\I)\spc
  \stable(R,I)\\
  \R(\stl,\stg,\stg') \Leftrightarrow \I(\C{true},\stl,\stg,\stg') 
        \wedge R(\stg,\stg') \spc
  c \elabsto \F\\
  \R_c(\stl,\stg,\stg') \Leftrightarrow \I(\C{false},\stl,\stg,\stg') 
        \wedge R(\stg,\stg') \spc
  \stable(\R_c,\F)\\
  \forall \stg.~ G(\stg, F(\emptyset,\stg) \gg \stg)\spc
  \forall \stg,\stg'.~I(\stg) \wedge G(\stg,\stg') \Rightarrow I(\stg')\\
}
{
  \rg{I,R}{\ctxn{i}{\I}{c}}{G,I}
}
\end{array}
\end{smathpar}
Automating the application of the \rulelabel{RG-Txn} rule for a
transaction requires automating the multiple implication checks in
the premise. While $R$, $\R$, $\R_c$, $\I$ and $\I$ are formulas in
first-order logic (FOL) with a relatively simple structure, $\F$
is an expression in the set language $\SL$
(Fig.~\ref{fig:logic-syntax}) with a possibly complex structure.
Fortunately, however, there exists a semantics-preserving translation
from $\SL$ to a restricted subset of first-order logic (FOL) that
lends itself to automatic reasoning.

>>>>

The correspondence between the inference rules and the RG judgment of
Sec.~\ref{sec:reasoning} is stated thus\footnote{The proof can be found in
the supplementary material.}:
\begin{theorem}
\label{thm:inference-sound}
  \emph{Forall} i,$R$,$I$,$c$,$\F$, if $\stable(\R,I)$ and $c \elabsto \F$,
  then:\\\vspace*{-0.2cm}
  \begin{smathpar}
  \begin{array}{c}
  \R \vdash \hoare{\lambda(\stl,\stg).~\stl=\emptyset \conj
  I(\stg)}{c}{\lambda(\stl,\stg).\stl = \F(\emptyset,\stg)}
  \end{array}
  \end{smathpar}
\end{theorem}
\noindent where the set expression $\F(\emptyset,\stg)$ has a natural
interpretation as discussed below.
% Where, ${\sf true} = \lambda(\stl,\stg).~true$ and $\stable(\R,I)
% \Leftrightarrow \forall\stl,\stg,\stg'. I(\stg) \conj
% \R(\stl,\stg,\stg') \Rightarrow \I(\stg')$.

@@

Theorem~\ref{thm:inference-sound} lets us replace the local judgment
of the \rulelabel{RG-Txn} rule (Fig.~\ref{fig:rg-rules}) by a state
transformer inference judgment. The soundness of a transaction's guarantee can now
be established w.r.t the effect $\F$ of the body. The
\rulelabel{RG-Txn} rule so updated is shown
below:
\begin{smathpar}
\begin{array}{c}
\RULE
{
  \stable(R,\I)\spc
  \stable(R,I)\\
  \R(\stl,\stg,\stg') \Leftrightarrow \I(\C{true},\stl,\stg,\stg') 
        \wedge R(\stg,\stg') \spc
  c \elabsto \F\\
  \R_c(\stl,\stg,\stg') \Leftrightarrow \I(\C{false},\stl,\stg,\stg') 
        \wedge R(\stg,\stg') \spc
  \stable(\R_c,\F)\\
  \forall \stg.~ G(\stg, F(\emptyset,\stg) \gg \stg)\spc
  \forall \stg,\stg'.~I(\stg) \wedge G(\stg,\stg') \Rightarrow I(\stg')\\
}
{
  \rg{I,R}{\ctxn{i}{\I}{c}}{G,I}
}
\end{array}
\end{smathpar}
Automating the application of the \rulelabel{RG-Txn} rule for a
transaction requires automating the multiple implication checks in
the premise. While $R$, $\R$, $\R_c$, $\I$ and $I$ are formulas in
first-order logic (FOL) with a relatively simple structure, $\F$
is an expression in the set language $\SL$
(Fig.~\ref{fig:logic-syntax}) with a possibly complex structure.
Fortunately, however, there exists a semantics-preserving translation
from $\SL$ to a restricted subset of first-order logic (FOL) that
lends itself to automatic reasoning.
